\cleardoublepage
\section*{Acknowledgement}
%\addcontentsline{toc}{section}{Acknowledgement}

I would like to thank the CEMEF laboratory, giving me the opportunity to study in the prestigious MINES ParisTech.
\newline
\newline
I would like to thank my directors, Dr. Charles-André Gandin and Pr. Michel Bellet, for their
guidance, support, and inspiration through my Ph.D. years.
I am grateful to Pr. Hervé Combeau and Pr. Markus Rettenmayr for the thesis report 
and the valuable expertise they brought to my work. I am also sincerely grateful to Pr. Florian Kargl for the examination of this dissertation.
This work has been supported by the European Space Agency. Its financial support for the research project CCEMLCC-2 is also gratefully acknowledged.
\newline
\newline
I would like to thank the members of our research group, especially Dr. Charles-André for all the technical discussions. 
I am also grateful to Dr. Tommy Carozzani for the valuable advices on my work and for the professional inspiration.
I thank also all the colleagues who influenced me in a way or in another: Jose, Shijia, Thi-Thuy-Mi, Alexis, Dorian, Sabrina, Xavier, Dr. Michel K, Hitti Drs and Masri Drs ... (and the list goes on).\newline
I am very thankful to Dr. Elie Hachem for the moral push in the last few miles before the thesis defence.
I am indebted to Dr. Frédéric Costes for continuously believing in my work and for giving me the opportunity
to continue my career in computational material science at TRANSVALOR.
\newline
\newline
I thank Rabih for being a great source of inspiration and discipline. The accomplishment of this work wouldn't have been possible without the unconditional support and love of the most important women in my life: my wife and my mother. 
\newline
\newline
Isn't life complex, complicated and beautiful at the same time ?